### 2018-12-04 chapters/02-synth.tex
beta 2! :)
maybe final version

\chapter{Evaluating the Effect of Homicide Prevention Strategies in São Paulo, Brazil: A Synthetic Control Approach\footnote{Forthcoming in \textit{Latin American Research Review}, 53(2), 2018. All data, code, and information required to replicate this study are available at \href{https://github.com/danilofreire/homicides-sp-synth}{https://github.com/danilofreire/homicides-sp-synth}.}}
\label{chap:synth}

>>>>

\chapter{Evaluating the Effect of Homicide Prevention Strategies in São Paulo, Brazil: A Synthetic Control Approach}
\label{chap:synth}
